DINO Methods for Style Transfer

### 2022-04-19 paper/Paper.tex
just quantitative
combined 4.2 with figure

\includegraphics[scale=0.35]{comparison}

In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image. But in both cases, certain details of the objects depicted in the content image are lost with experiment B being better at preserving features. For experiment A, we can see both the content and style losses decrease over time. Meanwhile, experiment B has a decrease style loss but its content loss first decreases and then increases before oscilating and staying overall the same.

Experiment C failed to learn style transfer. At the beginning of the training, it renders each content image with a color that roughly matches the style image, but over time, it started to copy the content image while completely ignoring the style image. After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are. As expected, the model's content loss decreases as it learns to copy the content images exactly and the style loss see no improvements.

During its training process, experiment D seems to be slowly learning to replicate the content image while not paying much attention to the style image. The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some occasional color losses. We see the content loss slowly decreases as training progresses while the style loss oscilates and shows no signs of improvement.

Finally, experiment E also failed. In early stages of the training, the model renders the content with many colored vertical strips and many features were lost. Eventually, the model started to output single-color images. We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.

>>>>

\begin{figure}
	\includegraphics[scale=0.35]{comparison}
	\caption{Style transfer results across different experiments.}
	\label{stylefig}
\end{figure}

In both experiments A and B, we can see that as training progresses, the model gradually learns to render the content image to the style of the style image. But in both cases, certain details of the objects depicted in the content image are lost. Experiment A seems to have less feature losses while experiment B produces style-transferred images that are closer to what the original style transferer produces (columns A, B, Original, figure \ref{stylefig}). For experiment A, we can see both the content and style losses decrease over time. Meanwhile, experiment B has a decreasing style loss but its content loss first decreases and then increases before oscilating more.

Experiment C failed to learn style transfer. At the beginning of the training, it renders each content image with a color that roughly matches the style image, but over time, it started to copy the content image while completely ignoring the style image. After 300k iterations, the model abruptly started to output single-colored images regardless of what the content and style images are (column C, figure \ref{stylefig}). As expected, the model's content loss decreases as it learns to copy the content images exactly and the style loss see no improvements.

During its training process, experiment D seems to be slowly learning to replicate the content image while not paying much attention to the style image. The resulting outputs started as poor-quality content images, but they slowly converged to the content images with some slight color variations (column D, figure \ref{stylefig}). We see the content loss slowly decreases as training progresses while the style loss oscilates and shows no signs of improvement.

Finally, experiment E also failed. In early stages of the training, the model renders the content with many colored vertical strips and many features were lost. Eventually, the model started to output single-color images (column E, figure \ref{stylefig}). We see no improvements in the style loss while the content loss abruptly drops at around 250k epochs when the model outputs became mostly single-colored images, then the content loss starts to oscillate again.
